Dissertation Proposal

### 2023-10-28 proposal.tex
lift lit review

@@

\section{Related Work}
\label{s:rel-work}

\paragraph{Misconceptions}

\paragraph{Goal Sentences}

\paragraph{Misinterpreters}

@@

>>>>

\section{Background: Misconceptions}

\section{Background: Program Behavior}

\section{Research Methodology}%
\label{s:research-methodology}

\subsection{\textbf{RQ1:} What are the misconceptions that are about program behavior, apply to most modern programming languages, and present (even) in students with prior programming backgrounds?}

This research question imposes three predicates on misconceptions:
\begin{enumerate}
  \item are about program behavior,
  \item apply to most modern programming languages, and
  \item present (even) in students with prior programming background
\end{enumerate}
The first predicate is the probably the most subtle, so I will talk
about it last. I approach the second predicate by modeling the
``consensus'' of modern programming language with SMoL. Because SMoL
represents the semantic core, misconceptions about SMoL presumably
also apply to most modern PLs. I approach the third and last predicate
by collecting data in population that very likely have prior experience.
For example, my priliminary results are build upon data collected in
a upper-year programming language course.

Let me come back to the first predicate. I would like to measure misconceptions
with tasks like the following:

[FILL]

I think tasks like the following
is best suited for measuring program-behavior misconceptions, in comparison
to tasks commonly found in literature.

% To find misconceptions about
% program behavior, I need to
% \begin{enumerate}
%   \item define what counts as a misconception about program behavior, and
%   \item describe how to find such a misconception
% \end{enumerate}
% Only conception that causes a student to predict a wrong result of a program
% counts as a misconception about program behavior. Here are a few example
% of misconceptions that I do \textit{not} consider about program behavior:
% \begin{enumerate}
%   \item \texttt{[1, 2, 3]} allocates 3 bytes. [CITE]
%   \item Variables reside on heap [CITE]
% \end{enumerate}
% I do not consider them because they go too deep into implementation
% details [FILL]. By limiting the scope to program behavior, I suspect
% the misconceptions I found would be more relevant to most reading,
% writing, and debugging tasks.

% Misconceptions about program behavior should not be specific to
% certain variable names, constants, or indentation. [FILL]

@@

@@

\section{Related Work}%
\label{s:related-work}

\subsection{Misinterpreters}
